---
title: "F-sabiti"
author: "Mine Çetinkaya-Rundel"
date: "20 April 2020"
output: 
  html_document:
    toc: yes
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

```{r load-packages}
library(tidyverse)
library(gghighlight)
library(knitr)
library(gt)
library(scales)
library(BenfordTests)
library(broom)
library(glue)
```

```{r load-data}
ecdc_raw <- read_csv("data/ecdc.csv")
```

```{r data-prep}
ecdc <- ecdc_raw %>%
  mutate(
    death_confirmed_ratio     = total_deaths / total_cases,
    death_confirmed_ratio_lag = lag(death_confirmed_ratio),
    diff_in_ratio             = death_confirmed_ratio - death_confirmed_ratio_lag,
    diff_in_ratio_abs         = abs(diff_in_ratio)
    ) %>%
  relocate(date, total_deaths, total_cases, 
           death_confirmed_ratio, diff_in_ratio, diff_in_ratio_abs) %>%
  group_by(location) %>%
  # after 10th confirmed death
  filter(total_deaths > 9) %>%
  # calculate days elapsed since 10th death
  mutate(days_elapsed  = as.numeric(date - min(date))) %>%
  ungroup()

ecdc_mt100_deaths <- ecdc %>%
  group_by(location) %>%
  summarise(max_tot_deaths = max(total_deaths)) %>%
  filter(max_tot_deaths > 100) %>%
  inner_join(ecdc, by = "location")

n_country_ecdc <- ecdc %>% distinct(location) %>% nrow()
n_country_ecdc_mt100_deaths <- ecdc_mt100_deaths %>% distinct(location) %>% nrow()

selected_countries <- c(
  "Turkey", 
  "China", 
  "Germany", 
  "Italy",
  "United States", 
  "United Kingdom"
)
```

COVID-19 data are downloaded from [Our World in Data's GitHub Repository](https://raw.githubusercontent.com/owid/covid-19-data/master/public/data/owid-covid-data.csv) on 20 April 2020.

The data has been filtered for dates after 10th death for each country. This means that countries with less than 10 total deaths due to COVID-19 so far are not included in the analysis, leaving `r n_country_ecdc` countries for analysis of all countries and `r n_country_ecdc_mt100_deaths` for analysis of all countries with more than 100 total deaths due to COVID-19.

This document addresses (though doesn't exactly answer) two questions:

1. Is the consistency in Turkey's cumulative deaths to cumulative confirmed cases ratio across consecutive days naturally occurring or might it indicate manipulation in numbers?

2. Can Benford's law be used to explore whether the numbers reported by Turkey are real or manipulated?

In certain points in the document we compare Turkey to all other countries or to all other countries with more than 100 deaths. In other points, to keep visualisations simple, we compare Turkey to a select list of countries consisting of `r glue_collapse(selected_countries[selected_countries != "Turkey"], sep = ", ", last = ", and ")`.

## Change in ratio over time

The figure below shows how the ratio of cumulative deaths to cumulative confirmed cases changes over time. Each line represents one country and we can see that this ratio behaves very differently for many countries. Turkey's trajectory does look pretty stable compared to some of the other countries highlighted in this plot, but this figure alone does not provide sufficient evidence to suspect manipulation in numbers.

```{r}
ggplot(ecdc) +
  geom_line(aes(x = days_elapsed, y = death_confirmed_ratio, group = location, color = location), size = 0.8) +
  gghighlight(location %in% selected_countries,
              use_direct_label = FALSE,
              unhighlighted_params = list(size = 0.2)) +
  facet_wrap(~ location) +
  guides(color = FALSE) +
  facet_wrap(~ location) +
  theme_minimal() +
  labs(
    x = "Days elapsed since 10th confirmed death",
    y = "Cumulative deaths / confirmed cases ratio",
    title = "Cumulative deaths / confirmed cases ratio",
    subtitle = "All countries"
  )
```

The figure below is another look at this same ratio, but only for countries that have had more than 100 deaths. Even though the number of countries plotted is halved, the trajectories look very similar what we saw in the figure above; limiting the analysis to countries with larger number of deaths does not provide any new insights.

```{r}
ggplot(ecdc_mt100_deaths) +
  geom_line(aes(x = days_elapsed, y = death_confirmed_ratio, group = location, color = location), size = 0.8) +
  gghighlight(location %in% selected_countries,
              use_direct_label = FALSE,
              unhighlighted_params = list(size = 0.2)) +
  facet_wrap(~ location) +
  guides(color = FALSE) +
  facet_wrap(~ location) +
  theme_minimal() +
  labs(
    x = "Days elapsed since 10th confirmed death",
    y = "Cumulative deaths / confirmed cases ratio",
    title = "Cumulative deaths / confirmed cases ratio",
    subtitle = "Countries with more than 100 deaths"
  )
```

### Daily change in ratio

Since suspicion of manipulation of numbers was due to little to no change in the cumulative deaths to confirmed cases ratio over a number of days in Turkey, it is worthwhile to explore the daily change in this ratio in other countries as well, and see how Turkey compares.

We can see that the daily change in the ratio approaches 0 for most countries as days elapsed increases.

```{r}
ggplot(ecdc) +
  geom_line(aes(x = days_elapsed, y = diff_in_ratio, group = location, color = location), size = 0.8) +
  gghighlight(location %in% selected_countries,
              use_direct_label = FALSE,
              unhighlighted_params = list(size = 0.2)) +
  facet_wrap(~ location) +
  guides(color = FALSE) +
  theme_minimal() +
  labs(
    x = "Days elapsed since 10th confirmed death",
    y = "Daily change in cumulative deaths / confirmed cases ratio",
    title = "Daily change in cumulative deaths / confirmed cases ratio",
    subtitle = "Change calculated as today's ratio minus yesterday's ratio for each day"
  )
```

Since we're interested in whether the ratio changes from day to day and how much, but not in which direction, it's actually more useful to look at the absolute value of daily change.

```{r}
ggplot(ecdc) +
  geom_line(aes(x = days_elapsed, y = diff_in_ratio_abs, group = location, color = location), size = 0.8) +
  gghighlight(location %in% selected_countries,
              use_direct_label = FALSE,
              unhighlighted_params = list(size = 0.2)) +
  facet_wrap(~ location) +
  guides(color = FALSE) +
  theme_minimal() +
  labs(
    x = "Days elapsed since 10th confirmed death",
    y = "Absolute daily change in cumulative deaths / confirmed cases ratio",
    title = "Absolute daily change in cumulative deaths / confirmed cases ratio",
    subtitle = "Change calculated as today's ratio minus yesterday's ratio for each day"
  )
```

### Number of consecutive days with no change

The following figure shows the number of consecutive days with no change, split by whether the country has had more than 100 total deaths or not. "No change" is calculated to the third decimal, e.g. suppose today country's cumulative death to confirmed cases ratio is 0.021 (rounded to 3 digits) and yesterday is was 0.021 (rounded to 3 digits) as well.

```{r fig.height=8}
ecdc %>%
  mutate(
    diff_in_ratio_rounded     = round(death_confirmed_ratio, 3) - round(death_confirmed_ratio_lag, 3),
    diff_in_ratio_abs_rounded = abs(diff_in_ratio_rounded)
  ) %>%
  filter(diff_in_ratio_abs_rounded == 0) %>%
  mutate(
    days_elapsed_lagged = lag(days_elapsed),
    days_elapsed_diff   = days_elapsed - days_elapsed_lagged
  ) %>%
  filter(days_elapsed_diff == 1) %>%
  arrange(location, days_elapsed) %>%
  relocate(location, days_elapsed, diff_in_ratio_abs_rounded) %>%
  group_by(location) %>%
  summarise(n_days_with_no_change = n()) %>%
  arrange(desc(n_days_with_no_change)) %>%
  mutate(
    mt_100_deaths = if_else(location %in% ecdc_mt100_deaths$location, "More than 100 total deaths", "10-100 total deaths"),
    turkey = if_else(location == "Turkey", TRUE, FALSE)
  ) %>%
  ggplot(aes(y = fct_reorder(location, n_days_with_no_change), x = n_days_with_no_change, fill = turkey)) +
  geom_col() +
  facet_grid(mt_100_deaths~., scales = "free_y") +
  guides(fill = FALSE) +
  scale_fill_manual(values = c("gray", "deeppink3")) +
  theme_bw() + 
  labs(
    x = "Number of consecutive days with no change",
    y = ""
  )
```

The following graphs shows the same, except here the ratios are rounded to 4 decimals (e.g. 0.0211).

```{r fig.height=4}
ecdc %>%
  mutate(
    diff_in_ratio_rounded     = round(death_confirmed_ratio, 4) - round(death_confirmed_ratio_lag, 4),
    diff_in_ratio_abs_rounded = abs(diff_in_ratio_rounded)
  ) %>%
  filter(diff_in_ratio_abs_rounded == 0) %>%
  mutate(
    days_elapsed_lagged = lag(days_elapsed),
    days_elapsed_diff   = days_elapsed - days_elapsed_lagged
  ) %>%
  filter(days_elapsed_diff == 1) %>%
  arrange(location, days_elapsed) %>%
  relocate(location, days_elapsed, diff_in_ratio_abs_rounded) %>%
  group_by(location) %>%
  summarise(n_days_with_no_change = n()) %>%
  arrange(desc(n_days_with_no_change)) %>%
  mutate(
    mt_100_deaths = if_else(location %in% ecdc_mt100_deaths$location, "More than 100 total deaths", "10-100 total deaths"),
    turkey = if_else(location == "Turkey", TRUE, FALSE)
  ) %>%
  ggplot(aes(y = fct_reorder(location, n_days_with_no_change), x = n_days_with_no_change, fill = turkey)) +
  geom_col() +
  facet_grid(mt_100_deaths~., scales = "free_y") +
  guides(fill = FALSE) +
  scale_fill_manual(values = c("gray", "red")) +
  theme_minimal() + 
  labs(
    x = "Number of consecutive days with no change",
    y = ""
  )
```

The stark difference between these two graphs show that how the values are rounded can change the story. It's possible the numbers are manipulated, but the measure of number of consecutive days of manipulation depends on rounding.

### Average absolute daily change in ratio

The following table lists the countries with the 9 lowest average absolute daily change in cumulative deaths / confirmed cases ratio.

```{r}
lowest_avg_diff_in_ratio_abs <- ecdc %>%
  select(days_elapsed, location, diff_in_ratio_abs) %>%
  group_by(location) %>%
  summarise(
    n = n(),
    avg_diff_in_ratio_abs = mean(diff_in_ratio_abs)
    ) %>%
  arrange(avg_diff_in_ratio_abs) %>%
  slice_head(n = 9)

lowest_avg_diff_in_ratio_abs %>%
  gt() %>%
  fmt_number(vars(avg_diff_in_ratio_abs), decimals = 5) %>%
  cols_width(vars(avg_diff_in_ratio_abs) ~ px(200)) %>%
  cols_label(
    location = "Country",
    n = "Number of days of data",
    avg_diff_in_ratio_abs = "Average absolute daily change in cumulative deaths / confirmed cases ratio"
    )
```

The following graph compares the trajectories of absolute daily change in ratio of these 9 countries to Turkey's.

```{r}
ggplot(ecdc) +
  geom_line(aes(x = days_elapsed, y = diff_in_ratio_abs, group = location, color = location), size = 0.8) +
  gghighlight(location %in% c(lowest_avg_diff_in_ratio_abs$location, "Turkey"),
              use_direct_label = FALSE,
              unhighlighted_params = list(size = 0.2)) +
  facet_wrap(~location) +
  guides(color = FALSE) +
  theme_minimal() +
  labs(
    x = "Days elapsed since 10th confirmed death",
    y = "Absolute daily change in cumulative deaths / confirmed cases ratio",
    title = "Absolute daily change in cumulative deaths / confirmed cases ratio",
    subtitle = "Change calculated as today's ratio minus yesterday's ratio for each day"
  )
```

In addition to looking at daily change, let's also see how Turkey compares to these countries with regards to the trajectory of the ratio.

```{r}
ggplot(ecdc) +
  geom_line(aes(x = days_elapsed, y = death_confirmed_ratio, group = location, color = location), size = 0.8) +
  gghighlight(location %in% c(lowest_avg_diff_in_ratio_abs$location, "Turkey"),
              use_direct_label = FALSE,
              unhighlighted_params = list(size = 0.2)) +
  facet_wrap(~location) +
  guides(color = FALSE) +
  facet_wrap(~ location) +
  theme_minimal() +
  labs(
    x = "Days elapsed since 10th confirmed death",
    y = "Cumulative deaths / confirmed cases ratio",
    title = "Cumulative deaths / confirmed cases ratio"
  )
```

<!-- -->

Let's repeat this analysis for countries with more than 100 total deaths.

```{r}
lowest_avg_diff_in_ratio_abs_mt100_deaths <- ecdc_mt100_deaths %>%
  select(days_elapsed, location, diff_in_ratio_abs) %>%
  group_by(location) %>%
  summarise(avg_diff_in_ratio_abs = mean(diff_in_ratio_abs)) %>%
  arrange(avg_diff_in_ratio_abs) %>%
  slice_head(n = 9)

lowest_avg_diff_in_ratio_abs_mt100_deaths %>%
  gt() %>%
  fmt_number(vars(avg_diff_in_ratio_abs), decimals = 5) %>%
  cols_width(vars(avg_diff_in_ratio_abs) ~ px(200)) %>%
  cols_label(
    location = "Country",
    avg_diff_in_ratio_abs = "Average absolute daily change in cumulative deaths / confirmed cases ratio"
    )
```

```{r}
ggplot(ecdc_mt100_deaths) +
  geom_line(aes(x = days_elapsed, y = diff_in_ratio_abs, group = location, color = location), size = 0.8) +
  gghighlight(location %in% c(lowest_avg_diff_in_ratio_abs_mt100_deaths$location, "Turkey"),
              use_direct_label = FALSE,
              unhighlighted_params = list(size = 0.2)) +
  facet_wrap(~ fct_relevel(location, c(lowest_avg_diff_in_ratio_abs_mt100_deaths$location, "Turkey"))) +
  guides(color = FALSE) +
  theme_minimal() +
  labs(
    x = "Days elapsed since 10th confirmed death",
    y = "Absolute daily change in cumulative deaths / confirmed cases ratio",
    title = "Absolute daily change in cumulative deaths / confirmed cases ratio",
    subtitle = "Change calculated as today's ratio minus yesterday's ratio for each day"
  )
```

```{r}
ggplot(ecdc_mt100_deaths) +
  geom_line(aes(x = days_elapsed, y = death_confirmed_ratio, group = location, color = location), size = 0.8) +
  gghighlight(location %in% c(lowest_avg_diff_in_ratio_abs_mt100_deaths$location, "Turkey"),
              use_direct_label = FALSE,
              unhighlighted_params = list(size = 0.2)) +
  facet_wrap(~ fct_relevel(location, c(lowest_avg_diff_in_ratio_abs_mt100_deaths$location, "Turkey"))) +
  guides(color = FALSE) +
  facet_wrap(~ location) +
  theme_minimal() +
  labs(
    x = "Days elapsed since 10th confirmed death",
    y = "Cumulative deaths / confirmed cases ratio",
    title = "Cumulative deaths / confirmed cases ratio"
  )
```

Turkey is in neither of these lists, indicating that whether we look at all countries or countries with more than 100 deaths, the variability in Turkey's daily ratios of confirmed deaths to confirmed cases isn't as low as some of the other countries.

### Daily deaths / confirmed cases

Ultimately, I think focusing on the ratio of cumulative deaths to confirmed cases is difficult to reason around. Comparing trajectories of daily deaths to daily confirmed cases, instead of cumulative versions of these numbers, can also be useful.

```{r}
p <- ecdc %>%
  mutate(death_confirmed_ratio2 = new_deaths / new_cases) %>%
  ggplot() +
  geom_line(aes(x = days_elapsed, y = death_confirmed_ratio2, group = location, color = location), size = 0.8) +
  gghighlight(location %in% selected_countries,
              use_direct_label = FALSE,
              unhighlighted_params = list(size = 0.2)) +
  facet_wrap(~ location) +
  guides(color = FALSE) +
  facet_wrap(~ location) +
  theme_minimal() +
  labs(
    x = "Days elapsed since 10th confirmed death",
    y = "Daily deaths / confirmed cases ratio",
    title = "Daily deaths / confirmed cases ratio",
    subtitle = "All countries"
  )

p
```

We can zoom in to this plot, limiting the y-axis to 0 to 0.1. Turkey's trajectory doesn't look too different than the initial trajectory of the US.

```{r}
p +
  ylim(0, 0.1)
```

## Benford's law

Imagine a large dataset, say something like a list of every country and its population. Benford's Law states that the leading digit will be a 1 more often than a 2. And 2s would probably occur more often than 3s, and so on. If a set of values were truly random, each leading digit would appear about 11% of the time (1/9), but Benford's Law predicts a logarithmic distribution. Since this phenomenon applies to naturally occurring numbers, it's used in fraudulent accounting/reporting detection.

```{r}
ecdc <- ecdc %>%
  mutate(
    digit_first.new_deaths = str_sub(new_deaths, 1, 1),
    digit_first.total_deaths = str_sub(total_deaths, 1, 1),
    digit_first.new_cases = str_sub(new_cases, 1, 1),
    digit_first.total_cases = str_sub(total_cases, 1, 1),
    digit_second.new_deaths = str_sub(new_deaths, 2, 2),
    digit_second.total_deaths = str_sub(total_deaths, 2, 2),
    digit_second.new_cases = str_sub(new_cases, 2, 2),
    digit_second.total_cases = str_sub(total_cases, 2, 2),
    digit_third.new_deaths = str_sub(new_deaths, 3, 3),
    digit_third.total_deaths = str_sub(total_deaths, 3, 3),
    digit_third.new_cases = str_sub(new_cases, 3, 3),
    digit_third.total_cases = str_sub(total_cases, 3, 3),
    digit_fourth.new_deaths = str_sub(new_deaths, 4, 4),
    digit_fourth.total_deaths = str_sub(total_deaths, 4, 4),
    digit_fourth.new_cases = str_sub(new_cases, 4, 4),
    digit_fourth.total_cases = str_sub(total_cases, 4, 4),
    digit_first_two.new_deaths = str_sub(new_deaths, 1, 2),
    digit_first_two.total_deaths = str_sub(total_deaths, 1, 2),
    digit_first_two.new_cases = str_sub(new_cases, 1, 2),
    digit_first_two.total_cases = str_sub(total_cases, 1, 2)
  )
```

### Distribution of digits

The figure below shows the distribution of first and second digits in new and total confirmed cases and in new and total deaths in numbers reported by Turkey.

```{r}
ecdc %>%
  filter(location ==  "Turkey") %>%
  select(location, contains("digit")) %>%
  pivot_longer(
    cols = -location, 
    names_to = c("digit_order", "value_type"),
    names_prefix = "digit_",
    names_sep = "\\.",
    names_ptypes = list(
      digit_order = factor(levels = c("first", "second", "third", "fourth", "first_two"), ordered = TRUE),
      value_type = factor(levels = c("new_cases", "new_deaths", "total_cases", "total_deaths"))
      ),
    values_to = "value"
    ) %>%
  filter(digit_order %in% c("first", "second")) %>%
  mutate(value = if_else(value == "", NA_character_, value)) %>%
  count(value_type, digit_order, value) %>%
  group_by(value_type, digit_order) %>%
  mutate(prop = n / sum(n)) %>%
  ggplot(aes(
    x = prop, 
    y = fct_rev(as.character(value)), 
    fill = value_type)
    ) +
  geom_col() +
  geom_text(aes(label = percent(prop, accuracy = 0.1)),
            hjust = -0.1,
            size = 3) +
  facet_grid(digit_order~value_type) +
  theme_bw() +
  scale_x_continuous(limits = c(0, 0.5), labels = label_percent(accuracy = 2)) +
  scale_fill_viridis_d() +
  labs(
    x = "Percentage",
    y = "Digit",
    title = "Leading digit frequencies in reported new/total confirmed cases and deaths in Turkey",
    subtitle = "First and second leading digits"
  ) +
  guides(fill = FALSE)
```

Literature also suggests that focusing on not just the first or second digit, but instead the combination of them (the string of two digits) is a more robust measure. The figure below shows the distribution of first two digits (together) in new and total confirmed cases and in new and total deaths in numbers reported by Turkey.

```{r fig.height=6}
ecdc %>%
  filter(location ==  "Turkey") %>%
  select(location, contains("digit")) %>%
  pivot_longer(
    cols = -location, 
    names_to = c("digit_order", "value_type"),
    names_prefix = "digit_",
    names_sep = "\\.",
    names_ptypes = list(
      digit_order = factor(levels = c("first", "second", "third", "fourth", "first_two"), ordered = TRUE),
      value_type = factor(levels = c("new_cases", "new_deaths", "total_cases", "total_deaths"))
      ),
    values_to = "value"
    ) %>%
  filter(digit_order == "first_two") %>%
  mutate(value = if_else(value == "", NA_character_, value)) %>%
  count(value_type, digit_order, value) %>%
  group_by(value_type, digit_order) %>%
  mutate(prop = n / sum(n)) %>%
  ggplot(aes(
    x = prop, 
    y = fct_rev(as.character(value)), 
    fill = value_type)
    ) +
  geom_col() +
  geom_text(aes(label = percent(prop, accuracy = 0.1)),
            hjust = -0.1,
            size = 3) +
  facet_grid(.~value_type, scales = "free_y") +
  theme_bw() +
  scale_x_continuous(limits = c(0, 0.5), labels = label_percent(accuracy = 2)) +
  scale_fill_viridis_d() +
  labs(
    x = "Percentage",
    y = "Digit",
    title = "Leading digit frequencies in reported new/total confirmed cases and deaths in Turkey",
    subtitle = "First two leading digits"
  ) +
  guides(fill = FALSE)
```

We can compare Turkey's numbers to a few other countries.

```{r fig.height=50}
ecdc %>%
  filter(location %in% selected_countries) %>%
  select(location, contains("digit")) %>%
  pivot_longer(
    cols = -location, 
    names_to = c("digit_order", "value_type"),
    names_prefix = "digit_",
    names_sep = "\\.",
    names_ptypes = list(
      digit_order = factor(levels = c("first", "second", "third", "fourth", "first_two"), ordered = TRUE),
      value_type = factor(levels = c("new_cases", "new_deaths", "total_cases", "total_deaths"))
      ),
    values_to = "value"
    ) %>%
  filter(digit_order == "first_two") %>%
  mutate(value = if_else(value == "", NA_character_, value)) %>%
  count(location, value_type, digit_order, value) %>%
  group_by(location, value_type, digit_order) %>%
  mutate(prop = n / sum(n)) %>%
  ggplot(aes(
    x = prop, 
    y = fct_rev(as.character(value)), 
    fill = value_type)
    ) +
  geom_col() +
  geom_text(aes(label = percent(prop, accuracy = 0.1)),
            hjust = -0.1,
            size = 3) +
  facet_grid(location~value_type, scales = "free_y") +
  theme_bw() +
  scale_x_continuous(limits = c(0, 0.5), labels = label_percent(accuracy = 2)) +
  scale_fill_viridis_d() +
  labs(
    x = "Percentage",
    y = "First two leading digits",
    title = "Leading digit frequencies in reported new/total confirmed cases and deaths in Turkey",
    subtitle = "First two leading digits"
  ) +
  guides(fill = FALSE)
```

### Chi-square testing for Benford's law

```{r}
alpha_bonferroni <- 0.05 / (n_country_ecdc_mt100_deaths * 2)
```

When data should conform to Benford’s law, a null-hypothesis rejection suggests that some form of data manipulation has taken place ([Joenssen, 2013][Joenssen_2013]). Rejection requires a low p-value, generally lower than 0.05. We will apply this test for numbers of new cases and new deaths for the `r n_country_ecdc_mt100_deaths` countries with more than 100 deaths. Since we're running many tests at once, we would apply a [Bonferroni correction][bonferroni], which reduces the threshold to `r format(round(alpha_bonferroni, 4), scientific = FALSE)`.

```{r fig.height=12}
benford_pvals <- ecdc %>%
  semi_join(ecdc_mt100_deaths, by = "location") %>% # only for countries with >100 deaths
  group_by(location) %>%
  select(location, new_cases, new_deaths) %>%
  summarise(pvalue = across(new_cases:new_deaths, ~tidy(chisq.benftest(.x))$p.value)) %>%
  unpack(pvalue) %>%
  mutate(new_cases = round(new_cases, 6), new_deaths = round(new_deaths, 6)) %>%
  pivot_longer(cols = -location, names_to = "value_type", values_to = "pvalue") %>%
  mutate(sig = if_else(pvalue < alpha_bonferroni, TRUE, FALSE))

ggplot(benford_pvals, aes(x = pvalue, y = fct_rev(location), label = pvalue)) +
  geom_point(color = "gray") + 
  geom_point(data = benford_pvals %>% filter(sig), aes(x = pvalue, y = location), color = "deeppink3") +
  geom_point(data = benford_pvals %>% filter(sig), aes(x = pvalue, y = location), color = "deeppink3", shape = "circle open", size = 3) +
  geom_label(data = benford_pvals %>% filter(sig), nudge_x = 0.03, hjust = 0) +
  facet_grid(.~value_type, scales = "free_x") +
  theme_bw() +
  labs(
    x = "p-value",
    y = "Country",
    title = "P-values for Pearson's Chi-squared Goodness-of-Fit Test for Benford's Law",
    subtitle = "For countries with more than 100 deaths"
  )
```

The test yields a positice result for values of new deaths in Turkey, but not new cases. This doesn't necessarily mean that the number are manipulated, but there is evidence to suggest that they don't follow Benford's law.

[Joenssen_2013]: https://www.statistics.gov.hk/wsc/CPS021-P2-S.pdf
[bonferroni]: https://en.wikipedia.org/wiki/Bonferroni_correction